### 2014-10-24 ApTranscriptome_TR.Rmd
changes to TR for final submission to PNAS

# arrange plots to make figure for manuscript
mh_plot_sub2 <- mh_plot_sub2 + ggtitle('A') + theme(plot.title = element_text(hjust=0))
mh_plot_sub1 <- mh_plot_sub1 + ggtitle('B') + theme(plot.title = element_text(hjust=0))

>>>>

# arrange plots to make figure for manuscript
mh_plot_sub1 <- mh_plot_sub1 + ggtitle('A') + theme(plot.title = element_text(hjust=0))
mh_plot_sub2 <- mh_plot_sub2 + ggtitle('B') + theme(plot.title = element_text(hjust=0))
